Bounds on the dimension of consistent convex surrogates

### 2020-05-26 neurips-20/cvx-flats.tex
Adding notation section

\subsection{Notation}

@@

\section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
\begin{definition}[Consistent: loss]\label{def:consistent-ell}
	A loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, and for all sequences of hypothesis functions $\{f_m : \X \to \R\}$,
	\begin{align*}
	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
	\end{align*}
\end{definition}
\bo{I guess we need the inf to be over a certain class of functions...the left and right side expectations need to be well-defined.}

@@

	We say $(L, \psi)$ is \emph{$\mu$-consistent with respect to the property} $\gamma$ if, for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and for all sequences $\{f_m: \X \to \R\}$, 
	\begin{equation}
	\E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~
	\end{equation}

>>>>

\subsection{Notation}
In this paper, we take the outcome set $\Y$ and consider $\simplex$ to be the simplex over $\Y$.
For $p \in \simplex$, let $\supp(p)$ be the support of $p$.
%discrete land
We use $\R$ to denote a report set; it is not necessary for $\Y = \R$.  
For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.
A loss $\ell : \R \times \Y \to \reals_+$ is \emph{discrete} if $|\R| < \infty$, and in general, we use $\ell$ to denote our \emph{target loss} for which we want to construct a consistent surrogate $L$.
For a distribution $p \in \simplex$, we denote the expected discrete loss for report $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
We denote the surrogate loss $L : \reals^d \times \Y \to \reals_+$, and typically denote a surrogate report with $u$.

Throughout this paper, we use tools from \emph{property elicitation} to understand the existence of consistent surrogate functions; a property is simply a function mapping distributions over the outcome simplex to reports.
Introduced in Section~\ref{subsec:properties}, a property $\Gamma: \simplex \to 2^\R \setminus \emptyset$ is denoted $\Gamma:\P \toto \R$.
We call a property \emph{set-valued} if there is a $p \in \P$ so that $|\Gamma(p)| > 1$, and \emph{single-valued} otherwise.
We use $\Gamma := \prop{L}$ to denote that $\Gamma$ is the (unique) property elicited by $L$.

Throughout this paper, we focus on characteristics of \emph{convex} surrogate losses.
When we say a loss $L(\cdot; p)$ is \emph{convex}, we mean that it is convex in its first argument for every $p \in \simplex$, which is equivalent to saying $L$ is convex in the report for every outcome $y \in \Y$.
Moreover, the regret of a loss $L(u; p)$ is the excess loss over the optimal; that is, $R_L(u,p) := L(u,p) - \inf_{u^*} L(u^*, p)$.

@@

\section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
\begin{definition}[Consistent: loss]\label{def:consistent-ell}
	A loss and link $(L,\psi)$ are consistent with respect to an original loss $\ell$ if, for all distributions $D$ over input and label spaces $\X \times\Y$, and for all sequences of measurable hypothesis functions $\{f_m : \X \to \R\}$,
	\begin{align*}
	\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y) &\implies \E_D \ell((\psi \circ f_m)(X), Y) \to \inf_f \E_D \ell((\psi \circ f)(X), Y)~.~
	\end{align*}
\end{definition}
\bo{I guess we need the inf to be over a certain class of functions...the left and right side expectations need to be well-defined.}

@@

	We say $(L, \psi)$ is \emph{$\mu$-consistent with respect to the property} $\gamma$ if, for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and for all sequences of measurable functions $\{f_m: \X \to \R\}$, 
	\begin{equation}
	\E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~
	\end{equation}
